Papers

### 2023-11-01 papers.qmd
add paper

## 2023
J. Brown, J. P. Davis, **J. D. Tucker**, J. G. Huerta, and K. Shuler, "Quantifying uncertainty in analysis of shockless dynamic compression experiments on platinum, Part 2: Bayesian model calibration", *Journal of Applied Physics*, submitted 2023.

@@

@@

D. Francom, **J. D. Tucker**, J. G. Huerta, K. Shuler, and D. Ries, "Elastic Bayesian Model Calibration", *Arxiv*, submitted, 2023. [arxiv preprint](https://arxiv.org/abs/2305.08834)

>>>>

## 2023
A. McCombs, M. A. Ausdemore, K. Goode, J. G. Huerta, K. Shuler, **J. D. Tucker**, A. Zhang, and D. Ries, “Inverse prediction of PuO2 processing conditions using Bayesian seemingly unrelated regression with functional data”, *Frontiers in Nuclear Engineering-Nuclear Materials*. submitted, 2023.

J. Brown, J. P. Davis, **J. D. Tucker**, J. G. Huerta, and K. Shuler, "Quantifying uncertainty in analysis of shockless dynamic compression experiments on platinum, Part 2: Bayesian model calibration", *Journal of Applied Physics*, in revision 2023.

@@

D. Francom, **J. D. Tucker**, J. G. Huerta, K. Shuler, and D. Ries, "Elastic Bayesian Model Calibration", *Arxiv*, in revision, 2023. [arxiv preprint](https://arxiv.org/abs/2305.08834)

@@
